Analysis of the included studies

### 2023-04-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed some paths

#The cleaned data without citations
compact_data_init <- read_rds(file.path(data_dir, 
                                        "review_data_compact_cleaned.rds")
                              )
```

@@

# The data with citations 
compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')

>>>>

#The cleaned data without citations
compact_data_init <- read_rds(file.path(data_dir, 
                                        "review_data_compact_cleaned.rds")
                              )

# The data with citations 
compact_data_with_citation_keys_init <- read_rds('../data/compact_data_with_citation_keys_cleaned.rds')
```

@@
